MS_Imp_Guidelines

### 2023-07-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
reworked abstract

To remain valid for longer, models should be continually updated and refined as new evidence emerges and healthcare systems evolve [@Jenkins2021; @@garcia2021cost]]. Ensuring that a model is regular reviewed to identify and implement required improvements is a receommended defence against model validity decay [@calder2018computational]. Key enablers of sustainable maintenance of open source research software are committed, adequately resourced core development team and active user community [@info:doi/10.2196/20028]. Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project. For more complex and multi-purpose CHEMs, particularly those designed to be incorporated into decision support systems, it may be better for development teams to adopt Agile Software Development [@beck2001manifesto], an approach that has been recommended for complex public health software projects [@10.3389/fpubh.2022.899874]. An Agile model will be less clearly specified in the initial project plan, but will instead continually develop in response to the requirements and feedback of users, who are provided with an initial, simplified working version of the model at the earliest feasible opportunity. Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements. Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable. It is important that verification checks are rerun with each model update, a task that can be automated using the software development practice of Continuous Integration [@CI2017].  The risk of model revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated model code and data.

>>>>

To remain valid for longer, models should be continually updated and refined as new evidence emerges and healthcare systems evolve [@Jenkins2021; @@garcia2021cost]. Ensuring that a model is regular reviewed to identify and implement required improvements is a receommended defence against model validity decay [@calder2018computational]. Key enablers of sustainable maintenance of open source research software are committed, adequately resourced core development team and active user community [@info:doi/10.2196/20028]. Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project. For more complex and multi-purpose CHEMs, particularly those designed to be incorporated into decision support systems, it may be better for development teams to adopt Agile Software Development [@beck2001manifesto], an approach that has been recommended for complex public health software projects [@10.3389/fpubh.2022.899874]. An Agile model will be less clearly specified in the initial project plan, but will instead continually develop in response to the requirements and feedback of users, who are provided with an initial, simplified working version of the model at the earliest feasible opportunity. Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements. Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable. It is important that verification checks are rerun with each model update, a task that can be automated using the software development practice of Continuous Integration [@CI2017].  The risk of model revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated model code and data.
